---
title: "R Notebook"
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

## Create a data frame

The code chunk appears:

```{r}
animals<-c("Snake","Bird","Dog","Spider")
animals
```

Type any R code in the chunk, for example:

```{r}
num_legs<-c(0,2,4,8)
num_legs
```

```{r}
animals_df<-data.frame(animals,num_legs)
animals_df
```

## Check and delete objects

Step1: use function \`ls()\` which returns a vector of character strings
giving the names of the objects in the environment.

```{r}
ls()
```

Step2: use the function `rm()` to remove the objects `num_legs` from the
working environment

```{r}
rm(num_legs)
```

Step3: Remove all objects in the working environment.

```{r}
rm(list=ls())
```

## Matrix operations

Use the `seq()`\` function to generate a sequence of numbers starting at
12 and decreasing to 2 in steps of -2. Call this vector
`x_vect. You may want to run ?seq or help(seq)` to help you do this

```{r}
x_vect<-seq(12,2,-2)
x_vect
```

Now convert the vector x vect into a matrix (with 2 rows and 3 coloumns)
called X, using the matrix() function. The result should look like this:

```{r}
X<-matrix(x_vect,2,3)
X
```

Next create a 2 by 2 matrix called Y consisting of a sequence of four
numbers from 1-4. The matrix Y should look like this:

```{r}
Y<-matrix(seq(4),2,2)
Y
```

In addition, create another 2 by 2 matrix called Z which looks as
follows:

```{r}
Z<-matrix(seq(4,10,2),2,2)
Z
```

Use the `t()` function to compute $Y^T$ and $Z^T$.

```{r}
YT<-t(Y)
ZT<-t(Z)
print(YT)
print(ZT)
```

**Matrix sums**. Compute the matrix sums $Y+Z$ and $Z+Y$ . The result in
both cases
should be the same. We call such operations commutative. This means that
reversing the order does not change the result.

```{r}
Y+Z
```

```{r}
Z+Y
```

**Matrix multiplication**. Compute the matrix products $YZ$ and $ZY$

(1) the results are not same

(2) matrix multiplication is not commutative.

```{r}
result1<-Y%*%Z
result2<-Z%*%Y
result1
result2
```

In addition, compute the matrix product $YX$ .

```{r}
result3<-Y%*%X
result3
```

Try to compute the matrix product $XY$ . We get the error message
because the non-conformable arguments

```{r}
result4<-X%*%Y
result4
```

**3. Matrix element-wise multiplication**

```{r}
result4<-Y*Z
result4
```

**4. Matrix inverse** get the result of $Y^{-1}$ via the `solve()`\`
function:

```{r}
M_inverse<-solve(Y)
M_inverse
```

Compute $Y^{-1}Y$ in R

```{r}
M_YY<-M_inverse%*%Y
M_YY
```

Compute $Y^{-1}X$.

```{r}
M_YX<-M_inverse%*%X
M_YX
```

### about solve()

use ?solve() to check the usage of solve()

```{r}
result<-solve(Y,X)
result
```
