---
title: "R Notebook"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

## Vector

```{r}
x<-c(3,7,4,2,1,2,-4,-5)
x
```

```{r}
y<-seq(5) #generate a sequence
y
```

```{r}
x[3] #access a element of a vector
```

```{r}
x[c(2,3)]
```

```{r}
x[1:4]   #access the first four element like this
```

```{r}
z<-c("Bristol","Bath","London")   #a vector of strings
z
```

```{r}
w<-c(TRUE,FALSE,TRUE,FALSE)  #a vector of Booleans
w
```

```{r}
a<-c(TRUE,3,"Bristol")   #You can't have a vector of mixed type!!!!
a
#they are all characters
```

-   查看vector的type

```{r}
mode(a)  # You can test the type like this
```

## 创建矩阵Matrix

```{r}
M<-matrix(seq(10),2,5)
M
#generate a 2 by 5 matrix
```

```{r}
M[2,3] #The third element of the second row
```

```{r}
M[,4] #or we can inspect the entire four column
```

-   判断是否是vector的类型

```{r}
is.vector(M[2,]) # we can check that a selected row or column is a vector
```

## Lists

```{r}
first_list<-list(TRUE,3,"Bristol")  # be different from vector, lists can be of mixed type
first_list
```

```{r}
second_list<-list(t_value=TRUE,num_value=3,city="Bristol") #lists members can be named like a dictionary
second_list$t_value
```

```{r}
second_list$num_value
```

```{r}
second_list$city
```

## Data frames 

Data frames are powerful objects for representing and manipulating **tabular data**

```{r}
city_name<-c("Bristol","Manchester","Birmingham","London")
population<-c(0.5,0.5,1,9)
first_data_frame<-data.frame(city_name,population)
first_data_frame
```

Unlike matrices,in data frames,

-   columns are named

-   different columns may be of different type

However,the cells within a column must be of the same type

## Arithmetic operations

```{r}
((4+2-1)*4/2)^2
```

```{r}
#在sample中，replace=TRUE代表一个样本可以出现好几次
a<-matrix(sample(1:10,6,replace=T),2,3) #a random 2 by 3 matrix
a
b<-matrix(sample(1:10,6,replace=T),2,3)
b
a*b
```

```{r}
a%*%t(b)
# t(b) computes the transpose of b
#%*% performs matrix multiplication
```

## Boolean operations

**NOT(complement)** **AND(conjunction)** **OR(disjunction)** **XOR(exclusive disjunction)**

```{r}
a<-c(TRUE,TRUE,FALSE,FALSE)
b<-c(TRUE,FALSE,TRUE,FALSE)
!a #not a
```

```{r}
a&b # a and b
```

```{r}
a|b # the inclusive or between a and b
```

-   异或运算：值不相等时为真

```{r}
xor(a,b) # the exclusive or between a and b
```

## Define a function

```{r}
is_prime<-function(num){
  stopifnot(is.numeric(num),num%%1==0,num>0)

  t_val<-TRUE

  if(num<2){
    t_val<-FALSE
  }else if(num>2){
    for(i in 2:sqrt(num)){
        if(num%%i==0){
            t_val<-FALSE
            break
        }
    }
  }
  return(t_val)
}
is_prime(39)

```

## Call-by-value semantics

In R, arguments in functions are passed with call-by-value semantics.

The value of a variable, but not its address, is passed to the function

```{r}
a<-seq(5,2)
demo_func_1<-function(x){
  x[2]<- -10
  print(x)
}
demo_func_1(a)
```

```{r}
a # Note that the value of a is unchanged
```

This facilitates a functional programming style with limited side effects

## Lazy evaluation

In lazy evaluation, a symbol can be defined (for example, in a function), but it will only be evaluated when it is needed

A more complicated example(**num_to_sub**)

```{r}
subtraction_function<-function(num_to_sub){
  output_function<-function(x){
    return (x-num_to_sub)
  } #a function with input x and output x minus num_to_sub
  return (output_function) #output this function
}
a<-1 #initialise
f1<-subtraction_function(a) #construct a function which subtracts
f1
print(f1(2))
```

```{r}
a<-2 # modify 
print(f1(2)) #doesn't change the function
```
Lazy evaluation enables effciency but has some surprising consequences.

```{r}
b<-1 #now initialise a new variable b
f2<-subtraction_function(b)
b<-2  # modify the value of b
print(f2(2)) #evaluating the function reveals that the second choice of b was used
b<-1
print(f2(2))
```
