---
title: "Assignment7"
author: "YujieWang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

# 1. Maximum likelihood estimates

## 1.1 Maximum likelihood estimates for Red tailed hawks

```{r}
library(Stat2Data)
data("Hawks")
Hawks%>%head(3)
```

### (Q1)

```{r}
RedTailedDf<-Hawks%>%filter(Species=="RT")%>%select(Weight,Tail,Wing)
RedTailedDf%>%head(5)
```

### (Q2)

```{r}
Tail<-RedTailedDf%>%pull(Tail)
n<-length(Tail)
mu_mle<-mean(Tail,na.rm=TRUE)
sigma_mle<-sd(Tail,na.rm=TRUE)*sqrt((n-1)/n)
print(mu_mle)
print(sigma_mle)
```

### (Q3)

```{r}
weights<-seq(mu_mle-3*sigma_mle,mu_mle+3*sigma_mle,sigma_mle*0.001)

colors<-c("MLE density"="red","Kernel density"="blue") #set color legend

estimated_density=data.frame(Length=weights,Density=dnorm(weights,mean=mu_mle,sd=sigma_mle))
plot_obj<-ggplot()+geom_line(data=estimated_density,aes(x=Length,y=Density,color="MLE density"))

#5.2 kernel density plot of the sample
plot_obj+geom_density(data=tibble(Tail),aes(x=Tail,color="Kernel density"))+
  labs(y="Tail length",color="colour")+theme_bw()+scale_color_manual(values=colors)
```

## 1.2 Unbiased estimation of the population variance

### (Q1)

```{r}
set.seed(0)
num_trials_per_sample_size<-1000
min_sample_size<-5
max_sample_size<-100
mu <- 1 #True mu
sigma_sqr <- 9  # sigma^2

#1. create data frame of all pairs of sample_size and trial
df<-crossing(trial=seq(num_trials_per_sample_size),
             sample_size=seq(from=min_sample_size,to=max_sample_size,by=5))

#2. For each pair,simulate a sequence of Gaussian random variables
df<-mutate(df,simulation=pmap(.l=list(trial,sample_size),
                              .f=~rnorm(.y,mean=mu,sd=sqrt(sigma_sqr))))

#3. For each sequence, compute the sample variance
sim_by_n_df<-mutate(df,sample_var=map_dbl(.x=simulation,.f=~var(.x)))

#4.1 create a scatter plot of sample variance
plot_obj<-ggplot()+labs(x="Sample size",y="Variance")+theme_bw()+
  geom_point(data=sim_by_n_df,
             aes(x=sample_size,y=sample_var,color="Sample",
                 linetype="Sample"),size=0.1)

#4.2 add a horizontal line displaying population variance
plot_obj<-plot_obj+geom_hline(aes(yintercept=sigma_sqr,color="Population",
                                  linetype="Population"),size=1)

#4.3 add Legends
plot_obj+
  scale_color_manual(name="Legend",values=c("Sample"="blue","Population"="red"))+
  scale_linetype_manual(name="Legend",values=c("Sample"="dashed","Population"="solid"))+
  scale_x_sqrt()
```

### (Q2)

### (Q3)（\*optional）

## 1.3 Maximum likelihood estimation with the Poisson distribution

### (Q1)

### (Q2)

### (Q3)

### (Q4)

### (Q5)(\*optional)

## 1.4 Maximum likelihood estimation for the exponential distribution

### (Q1)

### (Q2)

### (Q3)

### (Q4)

# 2. Confidence intervals

## 2.1 Student's t-confidence intervals

### (Q1)

### (Q2)

### (Q3)

## 2.2 Investigating coverage for Student's intervals

### (Q1)

### (Q2)

# 3. One Sample hypothesis testing

## 3.1 One sample t-test on penguins data

### (Q1)

## 3.2 Implementing a one-sample t-test

### (Q1)
